---
title: "Cribbage"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Notes:
0. Remove white boarder
1. See ration of saved image at bottom
2. I'm thinking for dimension no longer than 16 inched and wider than 5 inches
2.1 Probably 5x15 in.
3. I believe Barbra said holes are drilled 1/8 inch thick
4. I would like to use metal pegs and carve out the bottom to put a magnet there
6. Add skunk lines

# Loading Packages
```{r, warning=FALSE}
library(ggplot2)
library(ggthemes)
library(tidyverse)
# Hello World! Test 123
```

# Setting Parameters for sin functions
```{r}
ls = 1:145 # list of all dots including stop points
u = 8
b = (u-0)/145
r = (u-0)/145
a = 2.5
t = 0
w = (u-0)/145
```

# Functions
```{r}
#Finding Blue X Values
list_b = 
  function(ARGUMENT) {
    VALUE = b * ls
    return(VALUE)
  }
blue_x = list_b(b)

#Finding Red X Values
list_r = 
  function(ARGUMENT) {
    VALUE = r * ls
    return(VALUE)
  }
red_x = list_r(r)


#Finding Blue Y Values
blue = 
  function(ARGUMENT) {
    VALUE = sin(a * list_b(b) + t) + 1.125
    return(VALUE)
  }
blue_y_original = blue(list_b(b))
blue_y = blue(list_b(b))
blue_y[seq(6,145,6)] = NA # eliminates holes where we want spaces

#Finding Red Y Values
red = 
  function(ARGUMENT) {
    VALUE2 = sin(a * list_r(r) + t) + 1
    return(VALUE2)
  }
red_y_original = red(list_r(r))
red_y = red(list_r(r))
red_y[seq(6,145,6)] = NA # eliminates holes where we want spaces


#Finding Stopping Values

#Finding Blue Stopping X Values
blue_stoppers_x = 
  function(ARGUMENT) {
    VALUE = w * seq(6,145,6)
    return(VALUE)
  }
blue_stop_x = blue_stoppers_x(w)

#Finding Blue Stopper Y Values
blue_stoppers_y = 
  function(ARGUMENT) {
    VALUE = sin(a * blue_stoppers_x(w) + t) + 1.125
    return(VALUE)
  }
blue_stop_y = blue_stoppers_y(blue_stoppers_x(w))

#Finding Red Stopping X Values
red_stoppers_x = 
  function(ARGUMENT) {
    VALUE = w * seq(6,145,6)
    return(VALUE)
  }
red_stop_x = red_stoppers_x(w)

#Finding Red Stopper Y Values
red_stoppers_y = 
  function(ARGUMENT) {
    VALUE = sin(a * red_stoppers_x(w) + t) + 1
    return(VALUE)
  }
red_stop_y = red_stoppers_y(red_stoppers_x(w))
```

# Garbage Code
```{r, echo=FALSE}
#Old Data Frames

# names(wd)[1] = "input"
# names(wd)[2] = "output"
# names(wd)[3] = "col_input"
# 
# data = data.frame(blue_x,red_x,blue_y,red_y)
# df = cbind(stack(data[1:2]), stack(data[3:4]))
# names(df)[1] = "input"
# names(df)[2] = "col_input"
# names(df)[3] = "output"
# names(df)[4] = "col_output"
# df

# vec_w = c("white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white","white")
```

# Data Frames
```{r}
stp_blue = data.frame(blue_stop_x,blue_stop_y)
wd = data.frame(red_stop_x,red_stop_y)
blue_data = data.frame(blue_x,blue_y)
red_data = data.frame(red_x,red_y)
blue_data_clean = data.frame(blue_x,blue_y_original)
red_data_clean = data.frame(red_x,red_y_original)
```

# Plot
```{r, warning=TRUE}
# Parameters for lines
line_size = 2.5
dot_size = 1.75
alph_line = 0.5
alph_point = 5

# Parameter for strt line
top_start = 1.06

board = ggplot() + 
    geom_hline(yintercept = seq(0,2,0.5), color = "gray42") +
    geom_vline(xintercept = seq(0,8,1), color = "gray42") +
    # BLUE DOTS
    geom_point(data = blue_data, 
               aes(x=blue_x,y=blue_y), 
               color = "blue", 
               size = dot_size, 
               alpha = alph_point) +
    # RED DOTS
    geom_point(data = red_data, 
               aes(x=red_x,y=red_y), 
               color = "red", 
               size = dot_size, 
               alpha = alph_point) +
    # BLUE LINE
    geom_line(data = blue_data_clean, 
              aes(x=blue_x,y=blue_y_original), 
              color = "blue", 
              size = line_size, 
              alpha = alph_line) +
    # RED LINE
    geom_line(data = red_data_clean, 
              aes(x=red_x,y=red_y_original), 
              color = "red", 
              size = line_size, 
              alpha = alph_line) +
    # # BLUE SPACES
    # geom_point(data = stp_blue, 
    #            aes(x=blue_stop_x,y=blue_stop_y), 
    #            color = "black", 
    #            size = dot_size, 
    #            alpha = 5) +
    # # RED SPACES
    # geom_point(data = wd,
    #            aes(x=red_stop_x,y=red_stop_y),
    #            color = "black",
    #            size = dot_size,
    #            alpha = 5) +
    # BLUE START LINE
    geom_line(
              data = data.frame(
              rep(red_data_clean[1,1], 2) -0.0385,
              c(top_start,top_start-0.19)),
              aes(x = (rep(red_data_clean[1,1] -0.0385)),
                  y = c(top_start,top_start-0.19)
                  ),
              color = "blue", 
              size = line_size, 
              alpha = alph_line) +
    # RED START LINE
    geom_line(
              data = data.frame(
              rep(red_data_clean[1,1], 2),
              c(top_start,top_start-0.19)),
              aes(x = rep(red_data_clean[1,1]),
                  y = c(top_start,top_start-0.19)
                  ),
              color = "red", 
              size = line_size, 
              alpha = alph_line) +
    # BLUE START DOTS
    geom_point(
              data = data.frame(
              rep(red_data_clean[1,1], 3) -0.04,
              seq(1.04, 0.89, (-0.15)/2)
              ), 
              aes(x=rep(red_data_clean[1,1], 3) -0.04,
                  y=seq(1.04, 0.89, (-0.15)/2)), 
              color = "blue", 
              size = dot_size, 
              alpha = alph_line) +
    # RED START DOTS
    geom_point(
              data = data.frame(
              rep(red_data_clean[1,1], 3),
              seq(1.04, 0.89, (-0.15)/2)
              ), 
              aes(x=rep(red_data_clean[1,1], 3),
                  y=seq(1.04, 0.89, (-0.15)/2)), 
              color = "red", 
              size = dot_size, 
              alpha = alph_line) +
    # BLUE BEST OF 7 LINE
    geom_line(
              data = data.frame(
              c(0, 1.6), # this distance should be 0.45
              rep(0.02, 2)
              ),
              aes(x = c(0, 1.6),
                  y = rep(0.02, 2)),
              color = "blue",
              size = line_size,
              alpha = alph_line) +
    # RED BEST OF 7 LINE
    geom_line(
              data = data.frame(
              c(0, 1.6), # this distance should be 0.45
              rep(0.052, 2)
              ),
              aes(x = c(0, 1.6),
                  y = rep(0.052, 2)),
              color = "red",
              size = line_size,
              alpha = alph_line) +
    # BLUE BEST OF 7 DOTS
    geom_point(
               data = data.frame(
               seq(red_data[1,1], blue_data[28,1], 
                    (blue_data[28,1]-red_data[1,1])/6),
               rep(red_data[1,1], 7) -0.034), 
               aes(x=seq(red_data[1,1], blue_data[28,1], 
                        (blue_data[28,1]-red_data[1,1])/6),
                   y=rep(red_data[1,1], 7) -0.034), 
               color = "blue", 
               size = dot_size, 
               alpha = alph_line) +
    # RED BEST OF 7 DOTS
    geom_point(
               data = data.frame(
               seq(red_data[1,1], blue_data[28,1], 
                    (blue_data[28,1]-red_data[1,1])/6),
               rep(red_data[1,1], 7) -0.001), 
               aes(x=seq(red_data[1,1], blue_data[28,1], 
                        (blue_data[28,1]-red_data[1,1])/6),
                   y=rep(red_data[1,1], 7) -0.001), 
               color = "red", 
               size = dot_size, 
               alpha = alph_line) +
    # SKUNK LINE FOR BLUE
    geom_line(
              data = data.frame(
              x = rep(5.84 ,2),  # x
              y = c(1.9,2.1)     # y
              ), 
              aes(x = x, y = y)
              # ,
              # color = NULL,
              # size = NULL
    ) +
    scale_x_continuous(breaks = seq(0,8,2), 
                       limits = c(-0.05,8.1), 
                       expand = c(0, 0)) +
    scale_y_continuous(breaks = seq(0,2,1), 
                       limits = c(-0.025,2.15), 
                       expand = c(0, 0)) #might want to hard code max(blue_y)*1.05

    
board + 
  # theme_solarized_2(light = FALSE) + # Potential Theme
  theme(panel.background = element_rect(fill = "gray42"),
        axis.title.x = element_blank(),axis.title.y=element_blank(), # Removes Axis Title
        axis.text.x=element_blank(),axis.text.y=element_blank(),  # Removes Axis Numbers 
        axis.ticks.x=element_blank(),axis.ticks.y=element_blank(),
        axis.line = element_blank(),
        axis.line.y.left = element_blank(),
        plot.background = element_rect(fill = "gray42"), # how I made everything gray
        plot.margin = margin(0,0,-3,-3, "pt")            # how I made everything gray
        )# Removes Axis Ticks
        # scale_x_continuous(limits = c(0,8), expand = c(0, 0)) + # Trims Extra Parts of Graph
        

aspect_ratio <- 3 # Not Sure why but 3 scales us to 4 better than 4 does:(
height <- 5
ggsave("board.png", height = 5 , width = 5 * aspect_ratio)
library(png)
filename <- system.file("img", "board.png", package="png")
png("C:/Users/cyrus/OneDrive/Cribbage/board.png", 
    width = 15, 
    height = 5, 
    units = "in", 
    res = 300)
img <- readPNG(filename)
grid::grid.raster(img)


library(png)
img <- readPNG(filename)
grid::grid.raster(img)

filename <- system.file(getwd(), "board.png", package="png")  # or your own file
filename = "board.png"
temp <- tempfile(fileext = ".html")
writeLines(as.character(htmltools::img(src=knitr::image_uri(filename))), temp)
getOption("viewer")(temp)

print(image_read("board.png"), info = FALSE)
library(magick)
filename <- system.file("img", "Rlogo.png", package="png")

image_read(filename)
```

# Getting coordinates for holes
```{r}

# This is from finding_special_coordinates.R
blue_start_dots = data.frame(
  x = rep(red_data_clean[1,1], 3) -0.04,
  y = seq(1.04, 0.89, (-0.15)/2)
  )

red_start_dots = data.frame(
  x = rep(red_data_clean[1,1], 3),
  y = seq(1.04, 0.89, (-0.15)/2)
  )

blue_b7_dots = data.frame(
  x = seq(red_data[1,1], blue_data[28,1], 
      (blue_data[28,1]-red_data[1,1])/6),
  y = rep(red_data[1,1], 7) -0.034
  )

red_b7_dots = data.frame(
  x = seq(red_data[1,1], blue_data[28,1], 
      (blue_data[28,1]-red_data[1,1])/6),
  y = rep(red_data[1,1], 7) -0.001
  )

# removing spaces coordinates
blue_data = blue_data[-c(seq(6,145,6)),]
red_data = red_data[-c(seq(6,145,6)),]

# renaming columns
names(blue_data) = c("x", "y")
names(red_data) = c("x", "y")


# binding data sets
coordinates = rbind(
  blue_data, 
  red_data,
  blue_start_dots,
  red_start_dots,
  blue_b7_dots,
  red_b7_dots
  ) %>% cbind(
type = c(
  rep("blue holes",121),
  rep("red holes",121),
  rep("blue start",3),
  rep("red start",3),
  rep("blue overall",7),
  rep("red overall",7)
)
)
# rounding columns
coordinates[1] = round(coordinates[1],4)
coordinates[2] = round(coordinates[2],4)
write.csv(coordinates, file = "coordinates.csv")
```


